\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-16 bare_conf.tex
Update bare_conf.tex

\author{
\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
Povilas Daniu\v{s}is & Audrius Indriulionis \\
{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Department of  of Business Technologies and Entrepreneurship}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Vilnius, Lithuania} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: audrius.indriulionis@vgtu.lt} \\
& \\
Andrius Budrionis & Darius Plikynas \\
{\scriptsize Norwegian Centre for E-health Research} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
{\scriptsize University Hospital of North Norway} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Troms\o, Norway} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: andrius.budrionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
\end{tabular}
}

>>>>

\author{
\begin{tabular}[t]{c@{\extracolsep{2em}}c} 
Povilas Daniu\v{s}is & Andrius Budrionis \\
{\scriptsize Department of Business Technologies  and Entrepreneurship }& {\scriptsize Norwegian Centre for E-health Research}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize University Hospital of North Norway}\\
{\scriptsize Vilnius, Lithuania} & {\scriptsize Troms\o, Norway}\\
{\scriptsize email: povilas.daniusis@vgtu.lt} & {\scriptsize email: andrius.budrionis@vgtu.lt} \\
& \\
Audrius Indriulionis & Darius Plikynas \\
{\scriptsize Department of Business Technologies and Entrepreneurship} & {\scriptsize Department of Business Technologies and Entrepreneurship}\\ 
{\scriptsize Vilnius Gediminas Technical University} & {\scriptsize Vilnius Gediminas Technical University}\\
{\scriptsize Vilnius, Lithuania}} & {\scriptsize Vilnius, Lithuania}\\
{\scriptsize email: audrius.indriulionis@vgtu.lt} & {\scriptsize email: darius.plikynas@vgtu.lt} \\
\end{tabular}
}
